\section{Список литературы}

\begingroup
\let\clearpage\relax
\vskip-3cm
\begin{thebibliography}{9}

\bibitem{ApplyMagicSauce}
ApplyMagicSauce URL: https://applymagicsauce.com/demo

\bibitem{PersonalityInsights}
PersonalityInsights URL: https://personality-insights-demo.ng.bluemix.net/

\bibitem{Learning multiview embeddings of twitter users} 
Benton A., Arora R., Dredze M. Learning multiview embeddings of twitter users //Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics (Volume 2: Short Papers). – 2016. – Т. 2. – С. 14-19.

\bibitem{Developing age and gender predictive lexica over social media}
Sap M. et al. Developing age and gender predictive lexica over social media //Proceedings of the 2014 Conference on Empirical Methods in Natural Language Processing (EMNLP). – 2014. – С. 1146-1151.

\bibitem{Cross-platform differences in self-disclosure and trait prediction}
Jaika K., Guntuku S. C., Ungar L. H. Facebook vs. twitter: Cross-platform differences in self-disclosure and trait prediction. – 2018.

\bibitem{Inferring perceived demographics from user emotional tone and user-environment emotional contrast}
Volkova S., Bachrach Y. Inferring perceived demographics from user emotional tone and user-environment emotional contrast //Proceedings of the 54th Annual Meeting of the Association for Computational Linguistics (Volume 1: Long Papers). – 2016. – Т. 1. – С. 1567-1578.

\bibitem{Efficient estimation of word representations in vector space}
Mikolov T. et al. Efficient estimation of word representations in vector space //arXiv preprint arXiv:1301.3781. – 2013.

\bibitem{DeepWalk}
Perozzi B., Al-Rfou R., Skiena S. Deepwalk: Online learning of social representations //Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining. – ACM, 2014. – С. 701-710.

\bibitem{Node2Vec}
Grover A., Leskovec J. node2vec: Scalable feature learning for networks //Proceedings of the 22nd ACM SIGKDD international conference on Knowledge discovery and data mining. – ACM, 2016. – С. 855-864.

\bibitem{LINE}
Tang J. et al. Line: Large-scale information network embedding //Proceedings of the 24th international conference on world wide web. – International World Wide Web Conferences Steering Committee, 2015. – С. 1067-1077.

\bibitem{SDNE}
Wang D., Cui P., Zhu W. Structural deep network embedding //Proceedings of the 22nd ACM SIGKDD international conference on Knowledge discovery and data mining. – ACM, 2016. – С. 1225-1234.

\bibitem{Exact age prediction in social networks}
Perozzi B., Skiena S. Exact age prediction in social networks //Proceedings of the 24th International Conference on World Wide Web. – ACM, 2015. – С. 91-92.

\bibitem{Graph neural networks: A review of methods and applications}
Zhou J. et al. Graph neural networks: A review of methods and applications //arXiv preprint arXiv:1812.08434. – 2018.

\bibitem{GraphSAGE}
Hamilton W., Ying Z., Leskovec J. Inductive representation learning on large graphs //Advances in Neural Information Processing Systems. – 2017. – С. 1024-1034.

\bibitem{API VK}
API ВКонтакте URL: https://vk.com/dev

\bibitem{pandas}
Pandas URL: https://pandas.pydata.org/

\bibitem{linear regression}
Yan X., Su X. Linear regression analysis: theory and computing. – World Scientific, 2009.

\bibitem{sklearn}
scikit-learn URL: https://scikit-learn.org/

\bibitem{ESLII}
Hastie T., Tibshirani R., Friedman J. The elements of statistical learning: data mining, inference, and prediction, Springer Series in Statistics. – 2009.

\bibitem{svm}
Cortes C., Vapnik V. Support-vector networks //Machine learning. – 1995. – Т. 20. – №. 3. – С. 273-297.

\bibitem{svm regression}
Smola A. J., Schölkopf B. A tutorial on support vector regression //Statistics and computing. – 2004. – Т. 14. – №. 3. – С. 199-222.

\bibitem{knn}
Метод ближайших соседей URL: \\
http://www.machinelearning.ru/wiki/index.php?title=Метод\_ближай-шего\_соседа

\bibitem{random forest}
Breiman L. Random forests //Machine learning. – 2001. – Т. 45. – №. 1. – С. 5-32.

\bibitem{gradient boosting}
Friedman J. H. Greedy function approximation: a gradient boosting machine //Annals of statistics. – 2001. – С. 1189-1232.

\bibitem{xgboost}
XGBoost URL: https://xgboost.readthedocs.io/en/latest/

\bibitem{word2vec}
Mikolov T. et al. Efficient estimation of word representations in vector space //arXiv preprint arXiv:1301.3781. – 2013.

\bibitem{deepwalk lib}
deepwalk library URL: https://github.com/phanein/deepwalk

\bibitem{node2vec lib}
node2vec library URL: https://github.com/eliorc/node2vec

\bibitem{keras}
Keras URL: https://keras.io

\bibitem{stellargraph}
SteallarGraph URL: https://www.stellargraph.io

\end{thebibliography}
\endgroup

\clearpage